\section{Setup and experimental details}

\subsection{Pew research surveys}
\label{app:pew_collection}

Our dataset is derived from the annual Pew American Trends Panel (ATP) survey.
Below, we provide a brief summary of how the data collection process is conducted, and refer the reader to \url{pewresearch.org/our-methods/u-s-surveys/the-american-trends-panel/} and \url{pewresearch.org/our-methods/u-s-surveys/writing-survey-questions/} for more details.


\paragraph{Panelists.}

For ATP surveys, Pew relies on a group of about 10,000 participants within the US recruited over multiple years, many of whom take the survey repeatedly.
Each year, a subset of panelists are invited to take the ATP to reduce the burden on individual respondents.
Panelists are offered a paid incentive to participate in the survey.

Panelists are recruited by sending participation requests to a randomly-chosen address-based sample of households from USPS's Delivery Sequence File with concerted efforts to ensure representativeness of the sample. 
They also solicit input from households without internet access---either via phone or by providing them with tablets to take the survey.

\paragraph{Questionairre design.}
As stated on the Pew research website: "Perhaps the most important part of the survey process is the creation of questions that accurately measure the opinions, experiences and behaviors of the public...Designing the questionnaire is complicated because surveys can ask about topics in varying degrees of detail, questions can be asked in different ways, and questions asked earlier in a survey may influence how people respond to later questions."

Pew research selects pertinent topics for their surveys by monitoring the state of the nation and the world, and identifying issues that would be relevant to the public, media and policymakers.
They then go through an iterative process to build questions, often piloting them in focus groups, pre-interviews and cognitive testing.
The question wording is highly optimized to be clear, easy-to-understand, and not bias participants towards a particular answer. 

In order to identify valid choices for questions, Pew researchers often initially pilot open-ended surveys, and then use them to determine valid answer choices.

\paragraph{Data quality.}
Every survey, once designed is first tested out on a set of 60 ``fast'' panelists to flag any design errors.
Pew researchers also conduct data quality checks to identify issues with respondent satisfaction or the collected answers.
The ATP data is also accompanied with sample weights per individual to account for sampling bias and non-response over various stages of data collection.

Researchers have observed that human participants are sensitive to question and option ordering.
However, for questions with ordinal options ("Strongly agree"..."Strong disagree"), the option ordering is not randomized since they view it as conveying important information.

\subsection{Adapting ATP to \bname}
\label{app:survey_curation}
\label{app:taxonomize}

We derive our questions and human reference distributions based on \nsurveys ATP surveys over multiple years (2017-2021)---see Appendix Table~\ref{tab:survey_stats} for details.
The prefix in each survey name points to the wave in which it was collected.
We chose these surveys as they span a broad range of topics that might be pertinent for human-centric LM applications.
In Appendix Table~\ref{tab:survey_md}, we depict the demographic traits that we consider in our sub-group level analysis. 


\paragraph{Post-processing.}
As such, we directly extract multiple-choice questions from Pew ATP surveys and try to apply as little post-processing as possible. Some cases where we must filter or modify the questions are:
\begin{enumerate}
\item \emph{Cross-references:} Some questions make explicit references to context provided in a previous question. However, since we are presenting questions to LMs individually, we must modify every question to be self-contained. 
\item \emph{Variable-dependent questions:} We omit questions  where the phrasing of the question itself depends on a previous answer: ``In your answer to the previous question, you said \$ANSWER. Is this because....''. 
\item \emph{Formatting:} We fix any formatting issues that in questions to make them suitable for LMs (e.g., weird tokens or all capital words).
\item \emph{Lists:} Often, Pew surveys have lists where the same question is asked of many different variables. For instance, ``How much does each of the following affect your happiness in life? [A lot/.../Not at all]'' followed by a series of \$Xs such as ``money'', ``exercise''... In these cases, we restate the question to be self-contained, i.e., ``How much does \$X affect your happiness in life? [A lot/.../Not at all]'' in this case.
\end{enumerate}

As stated above, we try to keep our edits as minimal as possible.
In Appendix Table~\ref{tab:topic}, we describe the categories we manually taxonomize our dataset into for post-hoc topic-level analysis.
Note that questions may fall into multiple categories.

\input{Tables/survey_stats}
\input{Tables/survey_md}
\input{Tables/topic_info}
\input{Tables/steer_md}

For our steerability analysis in Section~\ref{sec:steerable}, we pick a subset of 500 questions where the subgroups under consideration frequently disagree.

\clearpage



\subsection{Models}
\label{app:models}
For our analysis, we use a series of models from OpenAI and AI21 labs, detailed in \ref{tab:models}.
Since the model training process is not always publicly known, we attempt to report this to the best of our knowledge.
Further documentation can be found \url{beta.openai.com/docs/model-index-for-researchers} and \url{docs.ai21.com/docs/}.
\input{Tables/models}

Once we prompt a model with a given question, we simply evaluate the log probabilities that each of the answer choices is the next-token.
We then take these token log probabilities for each answer, exponentiate and then normalize them to get the model opinion distribution, i.e.,
$D_M = [e^{lp_A}, e^{lp_B}, ...,] / sum([e^{lp_A}, e^{lp_B}, ...,])$


Currently, OpenAI and AI21 limit the number of log probabilities they return via their API to 100 and 10 respectively.
Thus, if one of the option choices (say `A') is not in the set of returned log probabilities, we attempt to bound it as follows.
Let's say the model returns a set of $K$ (100 or 64) token-log probabilities pairs $\{t_k, lp_k\}$.
We compute the total assigned mass as $p_{assigned} = \sum_{k \in K} e^{lp_k}$. The remaining mass is thus $p_{missing} = 1 - M$. We also find $p_min = \min_{k in K}e^{lp_k}$, i.e., the minimum probability assigned to any of the $K$ token choices.
Then, we assigning the missing token `A' the probability $min(p_{missing}, p_{min})$. Note that this is an upper bound on the true probability mass the model assigns to token `A'.

As a baseline, we also consider a random model that chooses one of the answers choices per question at random.

\subsection{Metrics}
\label{app:metric}
To compute the Wasserstein distance between human and LM opinion distributions to a question, we must map the to options to a metric space.
To do so, we leverage the ordinal structure of the options (as provided by Pew surveys).
For instance, we would map the set of options `Strong Agree', `Agree', `Maybe', `Disagree' and `Strong Disagree' to the integers 1 through 5.
We follow this approach in most cases, with the exception being questions for which the penultimate option is non-ordinal. For instance, if the choices were `Very good', `Very bad', and `Neither good nor bad'. In this case, we map the answers to 1, 2 and 1.5 respectively.

\subsection{Temperature scaling}
\label{app:temp}

In Section~\ref{sec:rep}, we compare the model opinion distribution to a sharpened version of its human counterpart.
This sharpening makes the human opinion distribution collapse towards its dominant mode.
To do so, we use the standard temperature scaling approach from \citet{Guo17}.
We use a temperature of 1e-3 in our analysis, but find that our results are fairly robust to the choice of temperature.
